Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS

### 2022-12-26 writing/CONUS_AOD.Rmd
Reorder paper text

@@

```{r error_envelope, echo=TRUE}
# error envelope for MAIAC is equivalent to that reported in AMT MAIAC publication
dt[, round(100 * proportions(table(y.sat > (y.ground - 0.05 - 0.1*y.ground) & y.sat < (y.ground + 0.05 + 0.1*y.ground))))]
# sure looks like we would have a much smaller error envelope (in both additive and multiplicative terms)
dt[, round(100 * proportions(table(y.ground.pred > (y.ground - 0.025 - 0.055*y.ground) & y.ground.pred < (y.ground + 0.025 + 0.055*y.ground))))]

# now with our error envelope function
envelope.sat <- empirical.error.envelope(dt, pred = "y.sat") 
head(envelope.sat)

# and for the corrected data
envelope.ground.pred <- empirical.error.envelope(dt, pred = "y.ground.pred") 
head(envelope.ground.pred)
```

@@

>>>>

## Error Envelope

The most important difference in our comparison of MAIAC AOD with AERONET observations versus prior validation analyses is the single-pixel comparison (substantially closer spatiotemporal matchups). Here we only include comparisons over CONUS which restricts the range of AOD and aerosol properties.

```{r error_envelope_AMT2018, echo=TRUE}
# error envelope for MAIAC is equivalent to that reported in AMT MAIAC publication
dt[, round(100 * proportions(table(y.sat > (y.ground - 0.05 - 0.1*y.ground) & y.sat < (y.ground + 0.05 + 0.1*y.ground))))]
```

```{r error_envelope, echo=TRUE}
# now with our error envelope function
envelope.sat <- empirical.error.envelope(dt, pred = "y.sat")
kable(head(envelope.sat), digits = 4)

# and for the corrected data
envelope.ground.pred <- empirical.error.envelope(dt, pred = "y.ground.pred")
kable(head(envelope.ground.pred), digits = 4)

```

@@

@@

A day with long-range transported smoke from Canadian wildfires.
